---
output: html_document
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
.text-container {
  max-width: 120ch;
  margin-left: auto;
  margin-right: auto;
}
.text-container2 {
  max-width: 75ch;
  margin-left: auto;
  margin-right: auto;
}
.vis-item .vis-item-overflow {
 overflow: visible;
 padding: 2px;
 padding-left: 5%;
 
}
.vis-item.vis-range .vis-item-content {
  display: inline;
}
.vis-item {
  font-size: 14px !important;
}
</style>

<br>

<div class = "text-container">

## __My PhD agenda 2.0__

#### Paul Schneider

#### Last updated: `r Sys.Date()`
**** 

```{r message=FALSE, warning=FALSE, include=FALSE}
# Gantt
library(gsheet)
library(RColorBrewer)
library(timevis)

# url_old <- 'https://docs.google.com/spreadsheets/d/1fAAtlsesJY_LpE1MCnS87oDqVebkaMLG4dLLoBAfRNA/edit?usp=sharing'
url <- 'https://docs.google.com/spreadsheets/d/1GNcpRpYV8m8R1nqxhkayimEzFyxPEXCNYt_qG7TnZoo/edit?usp=sharing'
raw_data <- gsheet2tbl(url)


# raw_data$subgroupOrder = 1:nrow(raw_data)

ColorizeGantt = function(gantttbl = raw_data){
  proj.colors = data.frame(group = unique(gantttbl$group),
                           style = brewer.pal(length(unique(gantttbl$group)), "Accent"))
  proj.colors = merge(gantttbl,proj.colors,by="group",sort = F)
  proj.colors$style = paste("background:",proj.colors$style)
  # proj.colors = paste(paste("'",proj.colors$col,"'", sep=""),sep="",collapse = ",")
  # proj.colors = paste("[",proj.colors,"]")
  return(proj.colors$style)
}
make_check_box = function(item,deadline="", checked = F){
  deadline = format(deadline,format="%d %b %Y")
  if(checked){
    cat('<tr>',
        '<td>',item,'</td>',
        '<td>',deadline,'<td>',
        '<td><input type="checkbox" name="" value="" checked></td>',
        '</tr>')      
  } 
  else {
    cat('<tr>',
        '<td>',item,'</td>',
        '<td>',deadline,'<td>',
        '<td><input type="checkbox" name="" value="" ></td>',
        '</tr>')      
    # cat('<input type="checkbox" name="" value="">',item,deadline,'<br>')      
  }
}




# create some labels etc
myGanttTable = raw_data[!is.na(raw_data$group),] 
myGanttTable = myGanttTable[!is.na(myGanttTable$start),]
myGanttTable$subgroup = myGanttTable$start
deadline = format(myGanttTable$end ,format ="%d.%m.")
myGanttTable$title = paste(
  "<b>",myGanttTable$content,"</b>",
  "<br><b>Deadline</b>:",deadline,"<br>",
  "<b>Status</b>:", myGanttTable$status,"<br>",
  "<b>Collaboration?</b>:", ifelse(is.na(myGanttTable$collaboration),"No",substr(myGanttTable$collaboration,1, 30))
  )
myGanttTable$style =  paste0(ColorizeGantt(myGanttTable),";","font-size:11px",sep=";")
myGanttTable$type = "range"



# create group ID and order
set_order = data.frame(content =  unique(myGanttTable$group),
                       id = as.numeric(unique(as.factor(myGanttTable$group)))
)
myGanttTable = myGanttTable[order(myGanttTable$start,decreasing = T),]

myGanttTable_group = data.frame(
  content = myGanttTable$group,
  id = as.numeric(as.factor(myGanttTable$group))
  )
myGanttTable_group = myGanttTable_group[!duplicated(myGanttTable_group$id),]
# myGanttTable$group = as.numeric(as.factor(myGanttTable$group))

myGanttTable_group = data.frame(content = myGanttTable$group)
myGanttTable_group = merge(myGanttTable_group,set_order,by="content")
myGanttTable$group = myGanttTable_group$id[match(myGanttTable$group, myGanttTable_group$content)]
myGanttTable_group = myGanttTable_group[!duplicated(myGanttTable_group$id),]
# myGanttTable_group$id = as.numeric(myGanttTable_group$content)


# config
config <- list(
  editable = F,
  align = "center",
  orientation = "center",
  snap = NULL,
  stack = T,
  subgroupStack = T,
  selectable	=T,
  margin = list(item = 5, axis = 20))

# plot
#ganttplot = timevis(myGanttTable, groups = myGanttTable_group,width = "100%",
#                    options = config,fit=T)
# htmlwidgets::saveWidget(ganttplot,file="ps_gantt.html",selfcontained = F)
# browseURL("ps_gantt.html")

tbl = myGanttTable
tbl$type[tbl$content == "Submission (aim)"] = "point"
tbl$type[tbl$content == "Submission deadline"] = "point"

# complete?
tbl$style[!is.na(tbl$completed)] = paste0(
  tbl$style[!is.na(tbl$completed)],
  "opacity: 0.75; color: black;")
# ongoing?
tbl$style[is.na(tbl$completed)] = paste0(
  tbl$style[is.na(tbl$completed)],
  "border: solid 1px black")
# published?
tbl$style[is.na(tbl$completed)] = paste0(
  tbl$style[is.na(tbl$completed)],
  "border: solid 1px black")

gantt = timevis(
  tbl, 
  groups = myGanttTable_group,
  width = "100%",
  options = config,
  fit=T
  )

# htmlwidgets::saveWidget(gantt,file="ps_gantt.html",selfcontained = F)
  
```


## Gantt chart

<strong><a href="https://docs.google.com/spreadsheets/d/1GNcpRpYV8m8R1nqxhkayimEzFyxPEXCNYt_qG7TnZoo/edit?usp=sharing" target="_blank">Edit data</a></strong>

</div> 

```{r echo=FALSE, message=FALSE, warning=FALSE}
gantt
```

<div class = "text-container2">
## Thesis chapter overview

### Preamble

Outline of the thesis, explaining how the question about the relationship between the individual and the group links the different parts of the thesis together

### Part 1: Introduction

  - <input type="checkbox"> 1.1 Historical context and review of health valuation methods
  - <input type="checkbox" checked> 1.2 Normative frameworks for the valuation of health, illustration of some critical unresolved issues in the context of health valuation in childre (draft)

### Part 2: Theoretical issues

- <input type="checkbox" checked> 2.1 Democratic tariff (published in HE)
- <input type="checkbox" checked> 2.2 Relative utilitarian preference aggregation
    - <input type="checkbox" checked> 2.2.1 Utility rescaling (UNPAc) (done, revise+resubmit MDM)
    - <input type="checkbox" checked> 2.2.2 Utility rescaling collaboration (report)
    - <input type="checkbox" checked> 2.2.3  Dead != 0. (revise+resubmit MDM)
- <input type="checkbox" checked> 2.3 The QALY is ableist (published in QoLR)

### Part 3: OPUF | Methodological development

- <input type="checkbox" checked> 3.1 The EQ-5D-5L OPUF Tool - Framework, tool development, and pilot
- <input type="checkbox" checked> 3.2 The EQ-5D-5L OPUF survey UK
  - <input type="checkbox" checked> 3.2.1 An alternative social value set
  - <input type="checkbox" checked> 3.2.2 Preference heterogeneity
- <input type="checkbox" > 3.3 The EQ-5D-5L OPUF survey Germany (public vs patient preferences)
-  <input type="checkbox" > 3.4 The 'OPUF Platform' 
- <span style = "color: darkgray"><input type="checkbox" > 3.5 The EQ-5D-Y OPUF survey UK</span>
- <span style = "color: darkgray"><input type="checkbox" > 3.6 The EQ-5D-5L OPUF survey South Africa</span>
- <span style = "color: darkgray"><input type="checkbox" > 3.7 OPUF vs PAPRIKA</span>



### Part 4: Synthesis

  - <input type="checkbox" > <mark>4.1 Simulation studies (?)</mark>


</div> 

<br><br>

****
&copy; Paul Schneider, 2022
<br><br><br>








